Stimjim: open source hardware for precise electrical stimulation

### 2019-05-12 benchmarking/paper/draft2.Rnw
fixed wrong gain in code from old (no longer correct) resistor values

x = c(paramMat[61:90,6], -paramMat[61:90,6])
y = t(sapply(res[seq(122,180,by=2)], function(x) c(x$sh.median,x$sl.median))/9750*1e6)
plot(x,y, main='Current accuracy', xlab='Target amplitude (uA)', ylab='measured amplitude (uA)', cex=0.75, col='red')
abline(a=0,b=1)

>>>>

x2 = c(paramMat[61:90,6], -paramMat[61:90,6])
y2 = t(sapply(res[seq(122,180,by=2)], function(x) c(x$sh.median,x$sl.median))/9750*1e6)
plot(x2,y2, main='Current accuracy', xlab='Target amplitude (uA)', ylab='measured amplitude (uA)', cex=0.75, col='red')
abline(a=0,b=1)

plot(x, as.vector(y)-x, pch=16, xlab='', ylab='')
par(new=TRUE)
plot(x2, as.vector(y2)-x2, pch=16, axes=F, col='red', xlab='',ylab='')
axis(1, col='red',line=2); 
axis(4, col='red')
